---
title: "Cognates Project"
author: "Bernhard Angele"
date: "29 May 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

rm(list = ls())


library(lme4)
library(yarrr)
library(beanplot)
library(MASS)
library(knitr)
library(tidyverse)

source("../Write sentences/corpus/bnc_functions.R")


ctr <- function(x) scale(x, scale = FALSE)

stim <- read_tsv("stimuli.tsv")
stim$item <- 1:nrow(stim)

stim <- stim %>% mutate(tar_bnc = find_bnc_freq(`Target word`), fill_bnc = find_bnc_freq(`Filler word`))

mean(as.numeric(stim$tar_bnc), na.rm = TRUE)

mean(as.numeric(stim$fill_bnc), na.rm = TRUE)

sd(as.numeric(stim$fill_bnc)-as.numeric(stim$tar_bnc), na.rm = TRUE)

cognate_properties <- read_csv("cognates_complete.csv")

vocab <- read_csv("vocabulary_tests_English_Spanish.csv")

prepare_data_frame <-  function(ixs){
  ixs_new <- ixs %>% left_join(stim, by = "item") %>%
    mutate(word = case_when(cond == 1 | cond == 3 ~ `Target word`,  
                            cond == 2 | cond == 4 ~ `Filler word`)) %>% # make  a column that gives the word in the target position no matter which condition we're in
    left_join(cognate_properties, by = c("word" = "English")) %>%
    left_join(vocab, by = "subj") %>%
    left_join(bnc_aggregate[bnc_aggregate$word %in% .$word,], by = "word", suffix = c("",".BNC")) %>%
    mutate(noise = factor(case_when(
      cond > 2 ~ "noise",
      cond <= 2 ~ "no_noise"), levels = c("no_noise", "noise"))
    ) %>%
    mutate(condition = factor(case_when(
      !`False Cognate` & (cond == 1 | cond == 3) ~ "cognate",
      `False Cognate` & (cond == 1 | cond == 3) ~ "false_cognate",
      !`False Cognate` & (cond == 2 | cond == 4) ~ "cognate_control",
      `False Cognate` & (cond == 2 | cond == 4) ~ "false_cognate_control"),
        levels = c("cognate","false_cognate","cognate_control", "false_cognate_control")))

  my_contrasts <- cbind(cognate_vs_control = c(-1,0,1,0), control_vs_fc_control = c(0,0,1,-1),
                          true_vs_false_cognate = c(-.5,.5,.5,-.5))
  contrasts(ixs_new$condition) <- zapsmall(t(ginv(my_contrasts)))
  colnames(contrasts(ixs_new$condition)) <- colnames(my_contrasts)
  contrasts(ixs_new$noise) <- contr.helmert


  return(ixs_new)
}
#c(C, F, CC, FC)
# Contrast 1: CC-C = c(-1,0,1,0)
# Contrast 2: FC-F = c(0,-1,0,1)
# Contrast 3: (CC-C) - (FC-F) = CC - C - FC + F = -C, F, CC, -FC c(-.5,.5,.5,-.5) 
# Can't do this because they're redundant (rank deficient)
# So instead do a contrasts comparing the targe twords: New Contrast 2: C-FC =  c(0,0,1,-1)

FFD <- read_csv("./IXS/COGFFD.IXS") %>% filter(!is.na(R1)) %>% prepare_data_frame()

GD <- read_csv("./IXS/COGGD.IXS") %>% filter(!is.na(R1)) %>% prepare_data_frame()

TVT <- read_csv("./IXS/COGTVT.IXS") %>% filter(!is.na(R1)) %>% prepare_data_frame()

#GOP <- read_csv("./IXS/COGGOP.IXS") %>% filter(!is.na(R1)) %>% prepare_data_frame()
```

## Study

- Idea: How do multilingual readers at different proficiency levels perceive cognates and false friends?
- Participants: Portuguese-Spanish-English trilinguals in Ceará, Brazil reading *English* (L3) sentences with embedded cognate or control words
- If there is no cross-talk between languages: 
    - Effects of visual similarity alone
    - Maybe stronger if you know the word in two languages?
- If there is an influence of native language/L2:
    - Effects of visual similarity plus effects of semantic overlap (e.g. "total" is faster to process than "sensible")
    - Effect should be stronger if you are better at the L2 (more conflict between "sensible" and the meansing of "sensitive")
    - All false friends with English were true cognates between Spanish and Portuguese
- Plus visual noise manipulation

## Example cognates and controls

```{r stimuli,results = "as.is", echo = FALSE}
kable(cognate_properties %>% dplyr::select(English, starts_with("Similar_word"), freq_per_million.x, starts_with("SOLAR")) %>% head)
```

## Example stimuli

```{r cars, echo = TRUE}
stim %>% 
  dplyr::select(experimental_sentence,  filler_sentence)%>% 
  head %>%
  kable
```

## Participant proficiency

```{r proficiency}
with(filter(vocab), qplot(english, spanish,  label = subj) + geom_text(nudge_y = .03))
```

Excluding participants 16, 34, 40 because of very low English proficiency



## Results: FFD

```{r FFD}

#beanplot(R2 ~ condition, data = GD %>% filter(!(subj %in% c(16,34,40))), beanlinewd = .1, log="",col="bisque", method="jitter")
pirateplot(R2 ~ condition + noise, data = FFD %>% filter(!(subj %in% c(16,34,40))), theme = 3)
ggplot(data = FFD %>% filter(!(subj %in% c(16,34,40))), aes(x = freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = FFD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = FFD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = FFD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = FFD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english)*freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
```

## Results: Gaze duration

```{r GD}

#beanplot(R2 ~ condition, data = GD %>% filter(!(subj %in% c(16,34,40))), beanlinewd = .1, log="",col="bisque", method="jitter")
pirateplot(R2 ~ condition + noise, data = GD %>% filter(!(subj %in% c(16,34,40))), theme = 3)
ggplot(data = GD %>% filter(!(subj %in% c(16,34,40))), aes(x = freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = GD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = GD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = GD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = GD %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english)*freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
```
## Results: TVT

```{r TVT}


#beanplot(R2 ~ condition, data = GD %>% filter(!(subj %in% c(16,34,40))), beanlinewd = .1, log="",col="bisque", method="jitter")
pirateplot(R2 ~ condition + noise, data = TVT %>% filter(!(subj %in% c(16,34,40))), theme = 3)
ggplot(data = TVT %>% filter(!(subj %in% c(16,34,40))), aes(x = freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = TVT %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = TVT %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = TVT %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english), y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
ggplot(data = TVT %>% filter(!(subj %in% c(16,34,40))), aes(x = ctr(spanish)*ctr(english)*freq_per_million, y = R2, colour = condition)) + geom_smooth()+ facet_grid(noise ~ .)
```
```{r ffdlmm, results="as.is"}
FFD.lmm <- lmer(data = FFD %>% filter(!(subj %in% c(16,34,40))), formula = R2 ~ condition*noise * ctr(english) * ctr(spanish)* ctr(1/freq_per_million) + (1|subj) + (1|item))

FFD.lm <- lm(data = FFD %>% filter(!(subj %in% c(16,34,40))), formula = R2 ~ condition*noise * ctr(english) * ctr(spanish)* ctr(freq_per_million))

summary(FFD.lmm)
```

```{r gdlmm, results="as.is"}

GD.lmm <- lmer(data = GD, formula = R2 ~ condition  *  noise + (1|subj) + (1|item))


GD.lmm <- lmer(data = GD, formula = R2 ~ condition  * noise * ctr(english) * ctr(spanish) + ctr(freq_per_million) + (1|subj) + (1|item))

summary(GD.lmm)
```

```{r tvtlmm, results="as.is"}
TVT.lmm <- lmer(data = TVT, formula = R2 ~ condition  *  noise + (1|subj) + (1|item))


tvt.lmm <- lmer(data = TVT, formula = R2 ~ condition * noise  + ctr(english) * ctr(spanish)* ctr(freq_per_million) + (1|subj) + (1|item))
summary(tvt.lmm)
```